ggplot and the venn diagram for the lefse bars !

### 2021-02-11 scripts/44_ggplot_venn_lefse.Rmd
updte

>>>>

## output a pretty ggplot version of the lefse bar plot

```{r}
make <- res_all %>% 
  filter(cohort == 'pull' & tbl == 'pathway') %>% 
  mutate(score = if_else(direction == 'no', -score, score)) %>% 
  mutate(feature = str_replace_all(feature, '_',' ')) 
  #mutate(feature = str_wrap(feature, width = 55, indent = 0, exdent = 0))

all_title_fs <- 20
axis_text_fs <- 16
make %>% 
  split(.$outcome) %>% 
  imap(~   ggplot(data = .x, aes(x = reorder(feature, score), y = score, fill = direction)) +
            geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
            coord_flip() +
            #scale_color_manual(values = c('#0099B4', '#AD002A'))  +
            #scale_fill_manual(values = c('#0099B4', '#AD002A')) +
            theme_classic() +
            theme(axis.title.y  = element_blank(), 
                  axis.title.x = element_text(size=axis_text_fs),
                  plot.title = element_text(size=all_title_fs),
                  axis.text.x = element_text(size=axis_text_fs),
                  legend.position="bottom") +
         scale_fill_manual(values = c('#0099B4','#AD002A')) +
            labs(title = str_glue('Response to {.y}') ,
                 y = 'Score')+ 
            ggsave(str_glue('../data/shotgun_output/humann3/pull_{.y}_pathway.pdf'), device = 'pdf', width = 8))
            #ggsave(str_glue('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/shotgun_results/NEW_humann3_version/pathway/pull_{.y}_pathway.pdf'), device = 'pdf', width = 12))

make %>% 
  filter(outcome == 'cr_d100') %>% 
  split(.$outcome) %>% 
  imap(~   ggplot(data = .x, aes(x = reorder(feature, score), y = score, fill = direction)) +
            geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
            coord_flip() +
            #scale_color_manual(values = c('#0099B4', '#AD002A'))  +
            #scale_fill_manual(values = c('#0099B4', '#AD002A')) +
            theme_classic() +
            theme(axis.title.y  = element_blank(), 
                  axis.title.x = element_text(size=axis_text_fs),
                  plot.title = element_text(size=all_title_fs),
                  axis.text.x = element_text(size=axis_text_fs),
                  legend.position="bottom") +
         scale_fill_manual(values = c('#ED0000','#00468B')) +
            labs(title = str_glue('Response to {.y}') ,
                 y = 'Score')+ 
            ggsave(str_glue('../data/shotgun_output/humann3/pull_{.y}_pathway.pdf'), device = 'pdf', width = 8))

# for above this is for the Italy excluded version 
```
